---
title: "Getting started with MMV"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with MMV}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

MMV can create a complete starter folder in one command:

```{r init, eval=FALSE}
library(MMV)
project <- mmviz_init("my-mmv-project")
project
```

The folder contains editable water-maze and minefield CSV files, a manifest,
an `outputs/` directory, and a standalone runner. Run it from any directory:

``` bash
Rscript my-mmv-project/run_mmviz.R
```

For a single file, use the unified plotting entry point:

```{r plot, eval=FALSE}
plot_mmviz(
  "my-mmv-project/data/watermaze.csv",
  task = "watermaze",
  out_file = "my-mmv-project/outputs/watermaze.png",
  cfg = list(style_mode = "builtin")
)
```

The task-specific functions remain available when you need their full intent
to be explicit:

```{r specific, eval=FALSE}
plot_watermaze("watermaze.csv", cfg = list(style_mode = "builtin"))
plot_minefield("minefield.csv", cfg = list(style_mode = "builtin"))
```

Standard CSV files require `subject_id`, `group`, `trial_id`, `frame`, `x`, and
`y`. Optional columns are `time_sec` and `event`. Batch manifests need `task`
and `input`; relative inputs are resolved from the manifest directory.
